---
title: "Simulation"
author: "Laura Cosgrove"
date: "11/27/2019"
output: github_document
---

# Recreate Araujo et al. simulation

$Y_{irs} = \lambda_i + \beta_{ir} + \epsilon_{irs} + Z_{irs}\tau_i$

where $Y_{irs}$ is the measured outcome for occasion s, $s = 1, 2 $ of cycle r, $r = 1, 2, .... k$ for patient i, $i = 1, 2, n$, and:

* $\lambda_i \sim N(\Lambda, \phi^2)$: Patient-specific mean of the outcome, drawn from a normal distribution with population mean of  $\Lambda$

* $\beta_{ir} \sim N(0, \gamma^2)$ : Within patient, within cycle (block) random noise

* $\epsilon_{irs} \sim N(0, \sigma^2)$ : Within patient, within cycle (block), within occassion  (independent of treatment) random noise

* $\tau_{i} \sim N(T, \psi^2)$: Where $Z_{irs}$ takes values $\frac{1}{2}$ when the occassion $s$ has treatment A and $-\frac{1}{2}$ when occassion $s$ has treatment B, The patient-specific for treatment effect, drawn from a normal population mean treatment effect of T. Therefore, an estimate for HTE (heterogeneity of treatment effect) is $\psi^2$.

"The sample size required for the proposed RCT is based on the primary outcome: change from baseline to  26 weeks on the PROMIS pain interference scale. Assuming that the minimally important difference is 0.4 SD difference (4 points) and that 10% of those who enter the study will not complete an endpoint and will therefore be assigned a change of 0, the full sample (endpoint completers plus non-completers) would need to show a 3.6-point difference in order for the completers to show a minimally important difference. Assuming a common standard deviation of 10 points, each group (Trialist app and usual care) would need to include 122 patients (244 in total) in order to have 80% power to detect a 3.6-point difference in means using a 2-group t-test with a 0.05 2-sided significance level."

Reference: PROMIS scores have a mean of 50 and standard deviation (SD) of 10 in a clinically relevant referent population. Assume division by 10 in the PREEMPT case.


1. Set parameter values

```{r}
#cycles, treatments, n
k = 4
s = 2
n = 122
nsim = 10000

#priors
##lambda_i
Lambda = 5
phi = 1

##beta_ir: choose sd that's lower than meaningful change (0.4)
gamma = 0.2

##epsilon_irs: choose same sd as within cycle change
sigma = 0.2

##tau: simulate T to be treatment effect under minimum importance
## simulate hte to be the variance if 1/4 of population had T
T = 4
##what if we had a population where in subpopulations, 1/4 had mean value, 1/4 had half of mean value, 1/4 had 1.5x mean value, 1/8 had 2x mean value, and 1/8 had no effect?
subpops = c(rep(4, 1000), rep(2, 1000), rep(6, 1000), rep(8, 500),rep(0, 500))
psi = sd(subpops)
```


2. Set the block randomization schedule for patients

```{r message = FALSE, warning = FALSE}
library(blockrand)
library(tidyverse)
set.seed(12)

#functions
block_rand = function(n_cycles = k, n_tx = s, char_tx = c("A", "B")) {

blockrand(n = n_tx*n_cycles, num.levels = n_tx, levels = char_tx, block.sizes = 1) %>% 
    pull(treatment)
  
}


get_n_blockrands = function(n_pt = n, n_cycles = k, n_tx = s, char_tx = c("A", "B")) {

rand_df <- tibble(id = 1:n_pt) %>% 
  mutate(rand = map(id, ~block_rand(n_cycles, n_tx, char_tx)))

rand_df
}

#Example Demonstration
block_rand()
rand_df <- get_n_blockrands()

rand_df %>% 
  unnest_longer(col = rand) %>% 
  group_by(id) %>% 
  mutate(occasion = 1:(s*k)) %>% 
  ggplot(aes(y = id, x = occasion, fill = rand)) +  geom_tile() + ggthemes::scale_fill_few() + ggthemes::theme_few()
  
seq_df <- rand_df %>% 
  unnest_longer(col = rand) %>% 
  group_by(id) %>% 
  mutate(cycle = rep(1:k, each = 2)) %>% 
  nest(-c("id", "cycle"), data = c(rand)) %>% 
  mutate(seq = map_chr(data, ~.x  %>% pull(rand) %>% stringr::str_flatten(., collapse = ", "))) %>% 
  select(-data) %>%
  mutate(seq = factor(seq)) 

seq_df %>% 
  group_by(cycle, seq) %>% count() %>% 
  ggplot(aes(x = seq, y = n)) +  geom_col(position = "dodge") + facet_grid(~cycle) + ggthemes::theme_few() + labs(title = "Distribution of cycle order in study", y = "Number of patients")
```

As shown, the order `(B, A)` or `(A, B)` is relatively evenly distributed among cycles.

3. Choose a patient i and simulate a value $\lambda_i$ and another value $\tau_i$. These are to be retained and used until all values for that patient have been generated.

```{r}
set.seed(11)

rand_df <- rand_df %>% 
  mutate(lambda = map_dbl(id, ~rnorm(1, mean = Lambda, sd = phi))) %>% 
  mutate(tau = map_dbl(id, ~rnorm(1, T, psi)))
```


4. Generate a value $\beta_{ir}$ for cycle r of patient i. This is to be retained and used for both occasions of that cycle of that patient’s course of treatments

```{r}
set.seed(10)

rand_df <- rand_df %>% 
  unnest_longer(col = rand) %>% 
  group_by(id) %>% 
  mutate(cycle = rep(1:k, each = 2)) %>% 
  nest(data = c(rand)) %>% rename(rand = data) %>% 
  mutate(beta = map_dbl(id, ~rnorm(1, mean = 0, sd = gamma)))

```


5. Generate a random number $X_{ir}$ from U(0,1) for that cycle.

```{r}
set.seed(9)

rand_df <- rand_df %>% 
  mutate(X = map_dbl(id, ~rnorm(1, mean = 0, sd = 1)))
```


6. Generate a value $\epsilon_{irs}$ for occasion s of cycle r for patient i.

```{r}
set.seed(8)

rand_df <- rand_df %>%
  mutate(rand = map(rand, ~unlist(.x))) %>% 
  unnest_longer(col = rand) %>% select(-rand_id) %>% 
  mutate(epsilon = map_dbl(rand, ~rnorm(1, mean = 0, sd = sigma)))
```


7. Calculate the response as the sum of the value of $\lambda_i$ for that patient $\beta_ir$ for that cycle, $\epsilon_{irs}$ for that occasion and the product of $\tau_i$ for that patient multiplied by $Z_irs$ for that occasion.

```{r}
rand_df <- rand_df %>% 
  mutate(Z = if_else(rand == "A", 1/2, -1/2)) %>% 
  mutate(Y = lambda + beta + epsilon + tau*Z) %>% 
  select(id, cycle, rand, Y, lambda, beta, epsilon, Z, tau)
```

`
```{r}
rand_df %>% 
  group_by(id, rand) %>% 
  summarize(Y_bar = mean(Y)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = rand, values_from = Y_bar) %>% 
  group_by(id) %>% 
  summarize(ITE = A - B) %>% 
  mutate(ATE = mean(ITE))  %>% 
  ggplot(aes(x = ITE)) + geom_histogram() + geom_vline(aes(xintercept = ATE, slope = 0), color = "red") + ggthemes::theme_few() + labs(title = "Distribution of ITE, with ATE plotted in red")
```

122 subjects x 4 cycles seems clearly enough to detect the true ATE under the chosen conditions.  Now, let's examine the operating characteristics more formally based on our analysis plan (a mixed effects model).

# Analyze simulated dataset

```{r}

```

