---
title: "Simulation"
author: "Laura Cosgrove"
date: "11/27/2019"
output: github_document
---

# Recreate Araujo et al. simulation

$Y_{irs} = \lambda_i + \beta_{ir} + \epsilon_{irs} + Z_{irs}\tau_i$

where $Y_{irs}$ is the measured outcome for occasion s, $s = 1, 2 $ of cycle r, $r = 1, 2, .... k$ for patient i, $i = 1, 2, n$, and:

* $\lambda_i \sim N(\Lambda, \phi^2)$: Patient-specific mean of the outcome, drawn from a normal distribution with population mean of  $\Lambda$

* $\beta_{ir} \sim N(0, \gamma^2)$ : Within patient, within cycle (block) random noise

* $\epsilon_{irs} \sim N(0, \sigma^2)$ : Within patient, within cycle (block), within occassion  (independent of treatment) random noise

* $\tau_{i} \sim N(T, \psi^2)$: Where $Z_{irs}$ takes values $\frac{1}{2}$ when the occassion $s$ has treatment A and $-\frac{1}{2}$ when occassion $s$ has treatment B, the patient-specific for treatment effect, drawn from a normal population mean treatment effect of T. Therefore, an estimate for HTE (heterogeneity of treatment effect) is $\psi^2$.

From our PREEMPT study setting:

"The sample size required for the proposed RCT is based on the primary outcome: change from baseline to  26 weeks on the PROMIS pain interference scale. Assuming that the minimally important difference is 0.4 SD difference (4 points) and that 10% of those who enter the study will not complete an endpoint and will therefore be assigned a change of 0, the full sample (endpoint completers plus non-completers) would need to show a 3.6-point difference in order for the completers to show a minimally important difference. Assuming a common standard deviation of 10 points, each group (Trialist app and usual care) would need to include 122 patients (244 in total) in order to have 80% power to detect a 3.6-point difference in means using a 2-group t-test with a 0.05 2-sided significance level."

Reference: PROMIS scores have a mean of 50 and standard deviation (SD) of 10 in a clinically relevant referent population. Assume division by 10 in the PREEMPT case.


1. Set parameter values

```{r}
#cycles, treatments, n
k = 4
s = 2
n = 34

#priors
##lambda_i
Lambda = 50
phi = 10

##beta_ir: choose sd that's lower than meaningful change (0.4)
gamma = 4

##epsilon_irs: choose same sd as within cycle change
sigma = 2

##tau: simulate T to be treatment effect under minimum importance
## simulate hte to be the variance if 1/4 of population had T
T = 4
psi = 1
```


2. Set the block randomization schedule for patients

```{r message = FALSE, warning = FALSE}
library(blockrand)
library(tidyverse)
set.seed(12)

#functions
block_rand = function(n_cycles = k, n_tx = s, char_tx = c("A", "B")) {

blockrand(n = n_tx*n_cycles, num.levels = n_tx, levels = char_tx, block.sizes = 1) %>% 
    pull(treatment)
  
}


get_n_blockrands = function(n_pt = n, n_cycles = k, n_tx = s, char_tx = c("A", "B")) {

rand_df <- tibble(id = 1:n_pt) %>% 
  mutate(rand = map(id, ~block_rand(n_cycles, n_tx, char_tx)))

rand_df
}

#Example Demonstration
block_rand()
rand_df <- get_n_blockrands()

rand_df %>% 
  unnest_longer(col = rand) %>% 
  group_by(id) %>% 
  mutate(occasion = 1:(s*k)) %>% 
  ggplot(aes(y = id, x = occasion, fill = rand)) +  
  geom_tile(color = "black") + ggthemes::scale_fill_few() + ggthemes::theme_few()
  
seq_df <- rand_df %>% 
  unnest_longer(col = rand) %>% 
  group_by(id) %>% 
  mutate(cycle = rep(1:k, each = 2)) %>% 
  nest(-c("id", "cycle"), data = c(rand)) %>% 
  mutate(seq = map_chr(data, ~.x  %>% pull(rand) %>% stringr::str_flatten(., collapse = ", "))) %>% 
  select(-data) %>%
  mutate(seq = factor(seq)) 

seq_df %>% 
  group_by(cycle, seq) %>% count() %>% 
  ggplot(aes(x = seq, y = n)) +  geom_col(position = "dodge") + facet_grid(~cycle) + ggthemes::theme_few() + labs(title = "Distribution of cycle order in study", y = "Number of patients")
```

As shown, the order `(B, A)` or `(A, B)` is relatively evenly distributed among cycles.

3. Choose a patient i and simulate a value $\lambda_i$ and another value $\tau_i$. These are to be retained and used until all values for that patient have been generated.

```{r}
set.seed(11)

rand_df <- rand_df %>% 
  mutate(lambda = map_dbl(id, ~rnorm(1, mean = Lambda, sd = phi))) %>% 
  mutate(tau = map_dbl(id, ~rnorm(1, T, psi)))
```


4. Generate a value $\beta_{ir}$ for cycle r of patient i. This is to be retained and used for both occasions of that cycle of that patient’s course of treatments

```{r}
set.seed(10)

rand_df <- rand_df %>% 
  unnest_longer(col = rand) %>% 
  group_by(id) %>% 
  mutate(cycle = rep(1:k, each = 2)) %>% 
  nest(data = c(rand)) %>% rename(rand = data) %>% 
  mutate(beta = map_dbl(id, ~rnorm(1, mean = 0, sd = gamma)))

```


5. Generate a random number $X_{ir}$ from U(0,1) for that cycle.

```{r}
set.seed(9)

rand_df <- rand_df %>% 
  mutate(X = map_dbl(id, ~rnorm(1, mean = 0, sd = 1)))
```


6. Generate a value $\epsilon_{irs}$ for occasion s of cycle r for patient i.

```{r}
set.seed(8)

rand_df <- rand_df %>%
  mutate(rand = map(rand, ~unlist(.x))) %>% 
  mutate(measure = list(c(1, 2))) %>% 
  unnest_longer(col = rand) %>% unnest_longer(col = measure) %>%  
  select(-rand_id) %>% 
  mutate(epsilon = map_dbl(rand, ~rnorm(1, mean = 0, sd = sigma)))
```


7. Calculate the response as the sum of the value of $\lambda_i$ for that patient $\beta_ir$ for that cycle, $\epsilon_{irs}$ for that occasion and the product of $\tau_i$ for that patient multiplied by $Z_irs$ for that occasion.

```{r}
rand_df <- rand_df %>% 
  mutate(Z = if_else(rand == "A", 1/2, -1/2)) %>% 
  mutate(Y = lambda + beta + epsilon + tau*Z) %>% 
  select(id, cycle, rand, Y, lambda, beta, epsilon, Z, tau)

rand_df
```

`
```{r}
rand_df %>% 
  group_by(id, rand) %>% 
  summarize(Y_bar = mean(Y)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = rand, values_from = Y_bar) %>% 
  group_by(id) %>% 
  summarize(ITE = A - B) %>% 
  mutate(ATE = mean(ITE))  %>% 
  ggplot(aes(y = ITE)) + geom_boxplot() + geom_hline(aes(yintercept = ATE, slope = 0), color = "red") + ggthemes::theme_few() + labs(title = "Distribution of ITE, with ATE plotted in red")

rand_df %>% 
  group_by(id, rand) %>% 
  summarize(Y_bar = mean(Y)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = rand, values_from = Y_bar) %>% 
  group_by(id) %>% 
  summarize(ITE = A - B) %>% 
  summarize(ATE = mean(ITE),
    sd_ATE = sd(ITE))  
```

122 subjects x 4 cycles seems clearly enough to detect the true ATE under the chosen conditions.  Now, let's examine the operating characteristics more formally based on our analysis plan (a mixed effects model).




# Analyze series of n of 1 trials

$$Y_{irs} = \lambda_i + \beta_{ir} + \epsilon_{irs} + Z_{irs}\tau_i$$
Set up functions to create the datasets:


```{r message = FALSE}
set.seed(1)
library(lme4)
analysis_df <- rand_df %>% 
  select(id, rand, cycle, Z, Y) %>% 
  ungroup()


mod = lme4::lmer(Y ~ 1 + Z + (1|id:cycle) + (Z|id) , data = analysis_df)
summary(mod)

```


Here, we can see that our parameter values are recovered to a large degree.

* We set $\phi$ in $\lambda_i \sim N(\Lambda, \phi^2)$, the standard deviation of the patient-specific mean of the outcome, drawn from a normal distribution with population mean of  $\Lambda$, to be `r phi`. Here, the corresponding estimate in the variance of the outcome is under random effects of `id`, where it is 7.57.

* We set $\Lambda$ in $\lambda_i \sim N(\Lambda, \phi^2)$, to be `r Lambda`. Here, the corresponding estimate in the mean of the outcome is under fixed effects, where it estimated as 45.65.

* We set $\gamma$ in $\beta_{ir} \sim N(0, \gamma^2)$, the within patient, within cycle (block) random noise, to be `r gamma`. Here, the corresponding estimate in the mean of the outcome is under random effects, `id:cycle` where it estimated as 3.47.

* We set $\sigma$ in $\epsilon_{irs} \sim N(0, \sigma^2)$, the within patient, within cycle (block), within occassion  (independent of treatment) random noise to be `r sigma`: here, it is the residual random effects variance, where it is estimated to be 2.11.

* We set T in $\tau_{i} \sim N(T, \psi^2)$, the population average treatment effect, to be `r T`. Here, it is estimated under the fixed effects Z term, as 3.79.

* We set $\psi$ in $\tau_{i} \sim N(T, \psi^2)$, the heterogeneity of treatment effect, to be `r psi`. Here, it is estimated under the random effects slope term of Z by treatment, as 7.96.


# Operating characteristics

For the above simulation, the confidence interval of T contains `r T`, and this will be the determination of treatment effect recovery for the operating characteristics:

```{r}
broom::tidy(mod, "fixed", conf.int = TRUE)

```

For the secondary outcome of estimating heterogeneity of treatment effects correctly, we will consider an interval of `r paste0(round(psi -2*0.4, 2) , ", ", round(psi +2*0.4, 2))` -- 2 minimally-important standard deviations from the true heterogeneity of treatment effect -- to be acceptable for the operating characteristics.

## Functions

```{r}
#function to block randomize
get_n_blockrands(n_pt = n, n_cycles = k, n_tx = s, char_tx = c("A", "B"))

#function to create lambda and tau
get_pt_level_effects = function(dat, pop_mean_Y = Lambda, pop_sd_Y = phi, pop_ave_TE = T, pop_sd_TE = psi ) {
  dat %>% 
  mutate(lambda = map_dbl(id, ~rnorm(1, mean = pop_mean_Y, sd = pop_sd_Y))) %>% 
  mutate(tau = map_dbl(id, ~rnorm(1, pop_ave_TE, pop_sd_TE)))
}

get_cycle_level_effects = function(dat, n_cycles = k, sd_Y_cycles = gamma) {
dat %>% 
  unnest_longer(col = rand) %>% 
  group_by(id) %>% 
  mutate(cycle = rep(1:n_cycles, each = 2)) %>% 
  nest(data = c(rand)) %>% rename(rand = data) %>% 
  mutate(beta = map_dbl(id, ~rnorm(1, mean = 0, sd = sd_Y_cycles)))
}

get_occasion_level_effects = function(dat, measurements = 2, sd_Y_occassion = sigma) {
dat %>%
  mutate(rand = map(rand, ~unlist(.x))) %>% 
  mutate(measure = list(1:measurements)) %>% 
  unnest_longer(col = rand) %>% unnest_longer(col = measure) %>%  
  select(-rand_id) %>% 
  mutate(epsilon = map_dbl(rand, ~rnorm(1, mean = 0, sd = sd_Y_occassion)))
}

get_tx_ind = function(dat, measurements = 2, char_tx = c("A", "B")) {
  dat %>% 
  mutate(Z = if_else(rand == char_tx[[1]], 1/2, -1/2)) 
}

get_outcome = function(dat) {
  dat %>% 
  mutate(Y = lambda + beta + epsilon + tau*Z) %>% 
  select(id, cycle, rand, Y, lambda, beta, epsilon, Z, tau)
}

```


```{r}
set.seed(11)
nsim = 100
sim_df <- tibble(sim = 1:nsim) %>% 
  mutate(data = map(sim, ~get_n_blockrands()))

sim_df <- sim_df %>% 
  mutate(data = map(data, ~get_pt_level_effects(dat = .x))) %>% 
  mutate(data = map(data, ~get_cycle_level_effects(dat = .x))) %>% 
  mutate(data = map(data, ~get_occasion_level_effects(dat = .x))) %>% 
  mutate(data = map(data, ~get_tx_ind(dat = .x))) %>% 
  mutate(data = map(data, ~get_outcome(dat = .x)))
```

## Model fitting for OC
```{r warning = FALSE, message=FALSE, fig.height = 10}
set.seed(12)

fit_mod <- function(dat) {
  lme4::lmer(Y ~ 1 + Z + (1|id:cycle) + (Z|id) , data = dat)
}

sim_mod <- sim_df %>% 
  mutate(mod = map(data, ~fit_mod(.x))) 

sim_mod <- sim_mod %>% 
  mutate(T_est = map_dbl(mod, ~broom::tidy(.x, "fixed", conf.int = TRUE) %>% filter(term == "Z") %>% pull(estimate))) %>% 
  mutate(T_clow = map_dbl(mod, ~broom::tidy(.x, "fixed", conf.int = TRUE) %>% filter(term == "Z") %>% pull(conf.low))) %>% 
  mutate(T_chigh = map_dbl(mod, ~broom::tidy(.x, "fixed", conf.int = TRUE) %>% filter(term == "Z") %>% pull(conf.high))) %>%
  mutate(hte_est = map_dbl(mod, ~broom::tidy(.x) %>% filter(term == "sd_Z.id") %>% pull(estimate))) %>% 
  mutate(T_in_T_CI = if_else(T_clow <= T & T_chigh >= T, 1, 0)) %>% 
  mutate(rej_sharp_null = if_else(T_clow <= 0 & T_chigh >= 0, FALSE, TRUE)) %>% 
  mutate(wrong_selection = if_else(T < 0 & T_chigh > 0 | T > 0 & T_chigh < 0, TRUE, FALSE)) %>% 
  mutate(hte_mse = sqrt((hte_est - psi)^2) ) %>% 
  mutate(ate_mse =  sqrt((T_est - T)^2) )

sim_mod %>% 
  count(rej_sharp_null)

sim_mod %>% 
  count(wrong_selection)

sim_mod %>% 
  count(T_in_T_CI)

```

```{r}
sim_mod %>% 
  ggplot(aes(x = hte_est)) + geom_density()+ geom_point(aes(y = 0, x = hte_est, alpha = rej_sharp_null)) + 
  ggthemes::theme_few()

```

```{r}
##final table
summary_mod = sim_mod %>% 
  summarize(Power_SharpNull = mean(rej_sharp_null),
            PIS =  mean(wrong_selection),
            Power_Estimate = mean(T_in_T_CI),
            MSE_ATE = mean(ate_mse),
            MSE_HTE = mean(hte_mse)) %>% 
  mutate(Method = "Mixed Effects Model") %>% 
  dplyr::select(Method, everything())

```

## Matched paired t test

```{r}
get_pair_test = function(dat){
D <- dat %>% 
  select(id, cycle, rand, Y) %>% 
  pivot_wider(names_from = rand, values_from = Y, values_fn = list(Y = mean)) 

t.test(D$A, D$B, paired = TRUE)
} 
test = get_pair_test(sim_df$data[[1]])

sim_tt <- sim_df %>% 
  mutate(ttest = map(data, ~get_pair_test(.x))) %>% 
  mutate(T_est = map_dbl(ttest, ~.x$estimate),
         T_clow = map_dbl(ttest, ~.x$conf.int[1]),
         T_chigh = map_dbl(ttest, ~.x$conf.int[2]),
         rej_sharp_null = map_dbl(ttest, ~.x$p.value),
         wrong_selection = if_else(rej_sharp_null < 0.05 & T_est < 0, TRUE, FALSE),
         rej_sharp_null = if_else(rej_sharp_null < 0.05, TRUE, FALSE),
         T_in_T_CI = if_else(T_clow <= T & T_chigh >= T, TRUE, FALSE),
         ate_mse = sqrt((T_est - T)^2))

summary_tt = sim_tt %>% 
  summarize(Power_SharpNull = mean(rej_sharp_null),
            PIS = mean(wrong_selection),
            Power_Estimate = mean(T_in_T_CI),
            MSE_ATE = mean(ate_mse, na.rm = TRUE),
            MSE_HTE = NA) %>% 
  mutate(Method = "Matched Pair T Test") %>% 
  dplyr::select(Method, everything())

```


## Metafor
The summary measures approach calculates the mean difference in outcome under B minus the mean difference in outcome under A per patient. In the literature this has been referred to as the basic estimator approach. After getting these summary measures, metaanalysis can be performed.
```{r}
library(metafor)
get_summary_measure <- function(dat) {
  dat %>% 
  select(id, cycle, rand, Y) %>% 
  group_by(id, cycle) %>% 
  pivot_wider(names_from = rand, values_from = Y, names_prefix = "t_", values_fn = list(Y  = mean)) %>% 
  summarize(d = t_A - t_B) %>% 
  summarize(d_mean = mean(d),
            d_var = var(d))
}

sim_df$data[[1]] %>% 
  select(id, cycle, rand, Y) %>% 
  group_by(id, cycle) %>% 
  pivot_wider(names_from = rand, values_from = Y, names_prefix = "t_", values_fn = list(Y  = mean)) %>%
  summarize(d = t_A - t_B) %>% 
  summarize(d_mean = mean(d),
            d_var = var(d))

data <- get_summary_measure(sim_df$data[[1]])

fit_meta_mod <- function(dat) {
  try_fit = try(metafor::rma.uni(dat$d_mean, dat$d_var, method = "REML"))
  class = class(try_fit)
  if(class == "try-error") {
    list(beta = NA,
                  ci.lb = NA,
                  ci.ub = NA, 
                  tau2 = NA) 
  }
    else {
      try_fit
  }
}
sim_ma <- sim_df %>% 
    mutate(sum_data = map(data, ~get_summary_measure(.x))) %>% 
    mutate(rma = map(sum_data, ~fit_meta_mod(.x))) %>% 
  mutate(T_est = map_dbl(rma, ~.x$beta)) %>% 
  mutate(T_clow = map_dbl(rma, ~.x$ci.lb)) %>% 
  mutate(T_chigh = map_dbl(rma, ~.x$ci.ub)) %>%
  mutate(hte_est = map_dbl(rma, ~sqrt(.x$tau2))) %>% 
  mutate(T_in_T_CI = if_else(T_clow <= T & T_chigh >= T, 1, 0)) %>% 
  mutate(rej_sharp_null = if_else(T_clow <= 0 & T_chigh >= 0, FALSE, TRUE)) %>% 
  mutate(wrong_selection = if_else(T < 0 & T_chigh > 0 | T > 0 & T_chigh < 0, TRUE, FALSE)) %>% 
  mutate(hte_mse = sqrt((hte_est - psi)^2) ) %>% 
  mutate(ate_mse =  sqrt((T_est - T)^2))


summary_ma = sim_ma %>% 
  summarize(Power_SharpNull = mean(rej_sharp_null, na.rm = TRUE),
            PIS = mean(wrong_selection, na.rm = TRUE),
            Power_Estimate = mean(T_in_T_CI, na.rm = TRUE),
            MSE_ATE = mean(ate_mse, na.rm = TRUE),
            MSE_HTE = mean(hte_mse, na.rm = TRUE)) %>% 
  mutate(Method = "Random Effects Meta-analysis") %>% 
  dplyr::select(Method, everything())

```

```{r}
fit_fmeta_mod <- function(dat) {
  metafor::rma.uni(dat$d_mean, dat$d_var, method = "FE")
}


sim_fma <- sim_df %>% 
    mutate(sum_data = map(data, ~get_summary_measure(.x))) %>% 
    mutate(frma = map(sum_data, ~fit_fmeta_mod(.x))) %>% 
  mutate(T_est = map_dbl(frma, ~.x$beta)) %>% 
  mutate(T_clow = map_dbl(frma, ~.x$ci.lb)) %>% 
  mutate(T_chigh = map_dbl(frma, ~.x$ci.ub)) %>%
  mutate(T_in_T_CI = if_else(T_clow <= T & T_chigh >= T, 1, 0)) %>% 
  mutate(rej_sharp_null = if_else(T_clow <= 0 & T_chigh >= 0, FALSE, TRUE)) %>% 
  mutate(wrong_selection = if_else(T < 0 & T_chigh > 0 | T > 0 & T_chigh < 0, TRUE, FALSE)) %>% 
  mutate(hte_mse = NA) %>% 
  mutate(ate_mse =  sqrt((T_est - T)^2))

summary_fma = sim_fma %>% 
  summarize(Power_SharpNull = mean(rej_sharp_null),
            PIS =  mean(wrong_selection),
            Power_Estimate = mean(T_in_T_CI),
            MSE_ATE = mean(ate_mse),
            MSE_HTE = mean(hte_mse)) %>% 
  mutate(Method = "Fixed Effects Meta-analysis") %>% 
  dplyr::select(Method, everything())

get_sum_table <- function(sim, name = "name") {
  sim %>% 
  summarize(Power_SharpNull = mean(rej_sharp_null),
            PIS =  mean(wrong_selection),
            Power_Estimate = mean(T_in_T_CI),
            MSE_ATE = mean(ate_mse),
            MSE_HTE = mean(hte_mse)) %>% 
  mutate(Method = name) %>% 
  dplyr::select(Method, everything())
}

```


# Summary 

```{r}
summary_mod %>% 
  bind_rows(summary_tt) %>% 
  bind_rows(summary_ma) %>% 
  bind_rows(summary_fma) %>% 
  pander::pander(digits = 3, 
               col.names = c("Method", "Proportion of studies \ where sharp null was rejected",
                            "Proportion of studies \ where the wrong treatment was recommended",
                            "Proportion of studies \ where the CI contained True Treatment effect",
                            "MSE, ATE", "MSE, HTE"
               ))


prep_df <- function(dat) {
  dat %>% 
  dplyr::select(sim, T_est, T_clow, T_chigh, rej_sharp_null) %>% 
  pivot_longer(-sim, names_to = "metric", values_to = "value")

}

prep_df(sim_mod) %>% 
  left_join(prep_df(sim_tt), by = c("sim", "metric"), suffix = c("_mx","_tt")) %>% 
  left_join(prep_df(sim_ma), by = c("sim", "metric")) %>% 
  left_join(prep_df(sim_fma), by = c("sim", "metric"), suffix = c("_ma","_fma")) %>% 
  pivot_longer(starts_with("value"), names_to = "method", values_to = "estimate", names_prefix = "value_") %>% 
  pivot_wider(names_from = "metric", values_from = "estimate") %>% 
  mutate(sim = forcats::fct_reorder(factor(sim), T_est)) %>% 
  mutate(rej_sharp_null = if_else(rej_sharp_null == 1, TRUE, FALSE)) %>% 
  ggplot(aes(x = sim, y = T_est, color = rej_sharp_null)) +
  geom_hline(aes(yintercept = T), color = "blue") + 
  facet_grid(~method, labeller = as_labeller(c("mx" = "Mixed Effects Model",
                                               "tt" = "Matched Paired t",
                                               "fma" = "Fixed Effects Meta-A",
                                               "ma" = "Random Effects Meta-A")) ) +
  geom_point() + 
  geom_errorbar(aes(ymin = T_clow, ymax = T_chigh)) +
  coord_flip() + 
  ggthemes::theme_few() + ggthemes::scale_color_few()


sim_mod %>% 
  dplyr::select(sim, hte_est) %>% 
  left_join(sim_ma %>%  dplyr::select(sim, hte_est), by = "sim", suffix = c("_Mixed Effects Model","_Random Effects Meta Analysis")) %>% 
  pivot_longer(starts_with("hte"), names_to = "method", values_to = "hte_est", names_prefix = "hte_est_") %>% 
  mutate(true_hte  = psi) %>% 
  ggplot(aes(y = hte_est, x = method)) + geom_boxplot() + 
  geom_point(aes(y = true_hte, color = true_hte)) +
  ggthemes::theme_few() + labs(x = "", y = "Estimated HTE", color = "True HTE")

```

<!-- ## refactoring  -->

<!-- ```{r} -->
<!-- m = 2 -->
<!-- df_blockrand <- get_n_blockrands() -->
<!-- char_tx = c("A", "B") -->
<!-- df_blockrand %>%  -->
<!--     get_pt_level_effects(dat = ., pop_mean_Y = Lambda, pop_sd_Y = phi, pop_ave_TE = T, pop_sd_TE = psi) %>%  -->
<!--     get_cycle_level_effects(dat = ., n_cycles = k, sd_Y_cycles = gamma) %>%  -->
<!--     get_occasion_level_effects(dat = ., measurements = m, sd_Y_occassion = sigma) %>%  -->
<!--     get_tx_ind(dat = ., char_tx = char_tx) %>%  -->
<!--     get_outcome(dat = .) -->


<!-- ``` -->

